LAGOS lake depth

### 2021-08-04 figures/02_depth_model.Rmd
linting

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
if(interactive()){
  setwd("figures")
}
source("../scripts/99_utils.R")
```

@@

tidy_importance <- function(x){
  # x <- dt_fits[[2]]$fit$fit
  res <- ranger::importance(x) %>%
  data.frame() %>% cbind(row.names(.), .[,1]) %>%
  setNames(c("percent_inc_mse", "variable"))
  row.names(res) <- NULL
  res <- res[,c(2, 1)]
  res <- arrange(res, percent_inc_mse)
  # res$variable <- factor(res$variable, levels = res$variable)
  res <- mutate(res, variable = as.character(variable))
  res <- mutate(res, variable = case_when(
    stringr::str_detect(variable, "maxdepth") ~ "trig_depth", 
    TRUE ~ variable)
    )
  res
}

dt_imp <- lapply(2:4, function(i) tidy_importance(dt_fits[[i]]$fit$fit))
model_names <- c("true_proxy", 
                 "proxy_true", 
                 "proxy_proxy")
dt_imp <- bind_rows(lapply(1:3, function(i){
  mutate(dt_imp[[i]], model = model_names[i])
  }))
dt_imp$model <- factor(dt_imp$model, levels = model_names)

@@

ggplot() + 
  geom_point(data = dt_imp, aes(percent_inc_mse, variable, color = model)) +   
  labs(color = "slope-distance\nmeasure") +
  geom_hline(linetype = 3, size = 1, colour = "gray",
                 yintercept = 1:nlevels(dt_imp$variable)) +
  theme(text = element_text(family="Times"),
        panel.background = element_blank(), panel.grid = element_blank(),
        panel.border = element_rect(fill = NA), # legend.position = "none", 
        axis.title.x = element_text(family = "sans", face = "bold", 
        vjust = -0.5, size = 10), 
        axis.text = element_text(family="sans",size = 9, 
                                 color = "black"), 
         legend.key = element_blank()) + 
        ylab("") + xlab("Percent Increase in Mean Square Error")
```

@@

gg_shape <- lapply(unique(dt$maxdepth), function(x){ 
  ggplot(data = dplyr::filter(dt, maxdepth == x)) + 
  geom_density(aes(x = resid, fill = shape_class), alpha = 0.75, adjust = 1.3) +
  scale_fill_manual(values = hue_pal()(3)[1:2]) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
        strip.background = element_blank(), 
        axis.text = element_text(size = 9.5),
        strip.text = element_blank(),
        plot.margin = unit(c(1.2,0.2,0.2,0.2), "cm"))  +
  guides(fill = guide_legend(nrow = 2))
  })
gg_shape[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_shape[[2]] + labs(fill = "Shape class") +
                                        theme(legend.direction = "horizontal") +
                                        guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none", 
                                        axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_shape      <- lapply(gg_shape, rm_legend)
gg_shape[[2]] <- gg_shape[[2]] + theme(axis.text = element_blank(), 
                                       axis.title = element_blank())
gg_shape[[3]] <- gg_shape[[3]] + theme(axis.title = element_blank())
gg_shape[[4]] <- gg_shape[[4]] + theme(axis.text.y = element_blank(), 
                                       axis.title = element_blank())

@@

          ncol = 2, rel_widths = c(0.1, 1)) %>%
  ggdraw() +
  draw_label("proxy", x = 0.06, y = 0.32, angle = 90, size = 10) +
  draw_label("true", x = 0.06, y = 0.75, angle = 90, size = 10) +
  draw_label("slope", x = 0.01, y = 0.55, size = 10, angle = 90) +
  draw_label("proxy", x = 0.8, y = 0.9, size = 10) +
  draw_label("true", x = 0.35, y = 0.9, size = 10) +
  draw_label("distance", x = 0.55, y = 0.96, size = 10)#  +
  # draw_label("Residual distribution", 
  #            x = 0.55, y = 0.99, size = 10, fontface = "bold")

gg_reservoir <- lapply(unique(dt$maxdepth), function(x){ 
  ggplot(data = dplyr::filter(dt, maxdepth == x)) + 
  geom_density(aes(x = resid, fill = reservoir_class), alpha = 0.75, adjust = 1.3) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
        strip.background = element_blank(), 
        strip.text = element_blank(),
        axis.text = element_text(size = 9.5),
        plot.margin = unit(c(1.2,0.2,0.2,0.2), "cm"))  +
  guides(fill = guide_legend(nrow = 2))
  })
gg_reservoir[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_reservoir[[2]] + labs(fill = "Reservoir class") +
                                        theme(legend.direction = "horizontal") +
                                        guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none", 
                                        axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_reservoir      <- lapply(gg_reservoir, rm_legend)
gg_reservoir[[2]] <- gg_reservoir[[2]] + theme(axis.text = element_blank(), 
                                       axis.title = element_blank())
gg_reservoir[[3]] <- gg_reservoir[[3]] + theme(axis.title = element_blank())
gg_reservoir[[4]] <- gg_reservoir[[4]] + theme(axis.text.y = element_blank(), 
                                       axis.title = element_blank())

@@

legend <- get_legend(
  # create some space to the left of the legend
  gg_noshape + theme(#legend.box.margin = margin(0, 0, 0, 12), 
                     legend.direction = "horizontal")
)

theme_opts <- theme(legend.position = "none", 
                    plot.title = element_text(size = 8))
cowplot::plot_grid(gg_noshape + theme_opts, 
                   gg_shape + theme_opts,
                   legend, 
                   rel_heights = c(1, 0.1)
                   )

```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
if (interactive()) {
  setwd("figures")
}
source("../scripts/99_utils.R")
```

@@

tidy_importance <- function(x) {
  # x <- dt_fits[[2]]$fit$fit
  res <- ranger::importance(x) %>%
    data.frame() %>% cbind(row.names(.), .[, 1]) %>%
    setNames(c("percent_inc_mse", "variable"))
  row.names(res) <- NULL
  res <- res[, c(2, 1)]
  res <- arrange(res, percent_inc_mse)
  # res$variable <- factor(res$variable, levels = res$variable)
  res <- mutate(res, variable = as.character(variable))
  res <- mutate(res, variable = case_when(
    stringr::str_detect(variable, "maxdepth") ~ "trig_depth",
    TRUE ~ variable)
  )
  res
}

dt_imp <- lapply(2:4, function(i) tidy_importance(dt_fits[[i]]$fit$fit))
model_names <- c("true_proxy",
  "proxy_true",
  "proxy_proxy")
dt_imp <- bind_rows(lapply(1:3, function(i) {
  mutate(dt_imp[[i]], model = model_names[i])
}))
dt_imp$model <- factor(dt_imp$model, levels = model_names)

@@

ggplot() +
  geom_point(data = dt_imp, aes(percent_inc_mse, variable, color = model)) +
  labs(color = "slope-distance\nmeasure") +
  geom_hline(linetype = 3, size = 1, colour = "gray",
    yintercept = 1:nlevels(dt_imp$variable)) +
  theme(text = element_text(family = "Times"),
    panel.background = element_blank(), panel.grid = element_blank(),
    panel.border = element_rect(fill = NA), # legend.position = "none",
    axis.title.x = element_text(family = "sans", face = "bold",
      vjust = -0.5, size = 10),
    axis.text = element_text(family = "sans", size = 9,
      color = "black"),
    legend.key = element_blank()) +
  ylab("") + xlab("Percent Increase in Mean Square Error")
```

@@

gg_shape <- lapply(unique(dt$maxdepth), function(x) {
  ggplot(data = dplyr::filter(dt, maxdepth == x)) +
    geom_density(aes(x = resid, fill = shape_class), alpha = 0.75, adjust = 1.3) +
    scale_fill_manual(values = hue_pal()(3)[1:2]) +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
      strip.background = element_blank(),
      axis.text = element_text(size = 9.5),
      strip.text = element_blank(),
      plot.margin = unit(c(1.2, 0.2, 0.2, 0.2), "cm"))  +
    guides(fill = guide_legend(nrow = 2))
})
gg_shape[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_shape[[2]] + labs(fill = "Shape class") +
  theme(legend.direction = "horizontal") +
  guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none",
  axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_shape      <- lapply(gg_shape, rm_legend)
gg_shape[[2]] <- gg_shape[[2]] + theme(axis.text = element_blank(),
  axis.title = element_blank())
gg_shape[[3]] <- gg_shape[[3]] + theme(axis.title = element_blank())
gg_shape[[4]] <- gg_shape[[4]] + theme(axis.text.y = element_blank(),
  axis.title = element_blank())

@@

  ncol = 2, rel_widths = c(0.1, 1)) %>%
  ggdraw() +
  draw_label("proxy", x = 0.06, y = 0.32, angle = 90, size = 10) +
  draw_label("true", x = 0.06, y = 0.75, angle = 90, size = 10) +
  draw_label("slope", x = 0.01, y = 0.55, size = 10, angle = 90) +
  draw_label("proxy", x = 0.8, y = 0.9, size = 10) +
  draw_label("true", x = 0.35, y = 0.9, size = 10) +
  draw_label("distance", x = 0.55, y = 0.96, size = 10) #  +
# draw_label("Residual distribution",
#            x = 0.55, y = 0.99, size = 10, fontface = "bold")

gg_reservoir <- lapply(unique(dt$maxdepth), function(x) {
  ggplot(data = dplyr::filter(dt, maxdepth == x)) +
    geom_density(aes(x = resid, fill = reservoir_class), alpha = 0.75, adjust = 1.3) +
    geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
      strip.background = element_blank(),
      strip.text = element_blank(),
      axis.text = element_text(size = 9.5),
      plot.margin = unit(c(1.2, 0.2, 0.2, 0.2), "cm"))  +
    guides(fill = guide_legend(nrow = 2))
})
gg_reservoir[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_reservoir[[2]] + labs(fill = "Reservoir class") +
  theme(legend.direction = "horizontal") +
  guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none",
  axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_reservoir      <- lapply(gg_reservoir, rm_legend)
gg_reservoir[[2]] <- gg_reservoir[[2]] + theme(axis.text = element_blank(),
  axis.title = element_blank())
gg_reservoir[[3]] <- gg_reservoir[[3]] + theme(axis.title = element_blank())
gg_reservoir[[4]] <- gg_reservoir[[4]] + theme(axis.text.y = element_blank(),
  axis.title = element_blank())

@@

legend <- get_legend(
  # create some space to the left of the legend
  gg_noshape + theme( # legend.box.margin = margin(0, 0, 0, 12),
    legend.direction = "horizontal")
)

theme_opts <- theme(legend.position = "none",
  plot.title = element_text(size = 8))
cowplot::plot_grid(gg_noshape + theme_opts,
  gg_shape + theme_opts,
  legend,
  rel_heights = c(1, 0.1)
)
```
